---
title: "Surface Water Data QC"
author: "Maddee Wiggins"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    code_folding: hide
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
#remotes::install_github("flowwest/CDECRetrieve")
library(CDECRetrieve)
library(dataRetrieval)
library(plotly)


knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE)

palette <- c("#999999", "#E69F00", "#56B4E9", "#F0E442", "#009E73", "#CC79A7")


```

# Surface Water Data QC

The purpose of this document is to QC the surface water data which is
periodically collected by Big Valley Rancheria using Rugged Troll 200.
The data have been corrected using barometric pressure.

### Load in BVR data

```{r}
surface_water <- readRDS(here::here('data', 'surface_water', 'surface_water_data_aggregated.RDS'))

stage_flow <- readxl::read_xlsx(here::here('data-raw', 'surface_water', 'Flow_vs_Depth_Table.xlsx'), sheet = "Data") 
```

### Load in 3rd Party data

```{r}
clearlake_level <- readNWISdv("11450000", "00065","2007-10-01", Sys.Date()) |> 
  mutate(WSE = X_00065_00003 + 1318.26,
         Date = as.POSIXct(Date, tz = "America/Los_Angeles"))

SW_bellhill_WB <- readxl::read_xlsx(here::here('data-raw', 'surface_water', 'water_board', 'PressureTransducer_and_Flow_Data_20230728.xlsx'), 
                                    sheet = "AC4-2023 Data", skip = 8)  |>
  mutate(Date = as.POSIXct(`Date Time (UTC)`),
         Date = with_tz(Date, "America/Los_Angeles"))

SW_kelsey_kelseyville_USGS <- read_csv(here::here('data-raw', 'surface_water', 'kelsey_kelseyville_usgs_stage_20240201.csv'))  |>
  mutate(Datetime = as.POSIXct(Datetime, format = "%m/%d/%Y %H:%M", tz = "America/Los_Angeles"),
         WSE = Stage + 1475.44)
```
#### 2024 data 
```{r}
# from HydroVu
adobe_ac4_2024 <- read_csv(here::here('data-raw', 'surface_water', 'water_board', 'AC4_2024_data', 'HydroVu_CLH_2024_Adobe_AC4_PT-529155_2024-01-01_15-38-08_Export.csv'), skip = 8) |> 
  janitor::clean_names() |> 
  mutate(depth_ft = depth_m*3.28084) |> 
  glimpse()

ggplot() + 
  geom_line(data = adobe_ac4_2024, aes(x = date_time, y = depth_ft)) + theme_minimal()+
  ggtitle("AC4") + 
  ylab('Depth (ft)') + 
  xlab('Date')
```

```{r}
acf_depth <- CDECRetrieve::cdec_query("ACF", "204", "E", "2024-01-01", "2025-01-01") 

acf_depth_adj <- acf_depth |> 
  # per Lester Grade DWR
  # TODO: double check that this has occured in the database. 
  mutate(depth_ft_adjust = parameter_value + 5.08,
         depth_ft = depth_ft_adjust - 30.5,
         wse = parameter_value + 1300 + 5.08) |>  
  glimpse()

# TODO: need to subtract out the WSE

ggplot() + 
  geom_line(data = acf_depth_adj, aes(x = datetime, y = depth_ft)) + theme_minimal()+
  ggtitle("ADOBE CRK NR FINLEY AT SODA BAY RD, DWR") + 
  ylab('Depth (ft)') + 
  xlab('Date') 
 # labs(caption = "depth adjusted by +5.08 feet per necessary correction through communcation with Lester Grade, DWR")

```

**Timeframe:**

Surface Water Data: `r min(surface_water$datetime)` -
`r max(surface_water$datetime)`

**Completeness of record throughout timeframe:** Complete

**Sampling Location**:

Surface Water Data: Pressure transducers are located in the creek bed at
Bell Hill Rd, Argonaut Rd, Soda Bay Rd, Adobe Reservoir, and Highland
Springs Reservoir.

### Raw Data

```{r}
surface_water |> 
  group_by(name) |>
  summarise(min_date = min(datetime),
            max_date = max(datetime),
            n_records = n()) |> 
  knitr::kable()
```

```{r fig.height=9, fig.width=11}
ggplot(data = surface_water, aes(x = datetime, y = depth_ft, color = name)) +     
  geom_line() + 
  scale_color_manual(values = palette) +
  labs(color = "Transducer Location", x = "Datetime", y = "Water Depth (ft)") +
  theme_minimal() +
  facet_wrap(~name, scales = "free_y")
```

### Previous QC

This analysis was performed for dates 2018 to 2023 and explained in
detail in the report: [Big Valley Subbasin Data Analysis]
Memo)(<https://drive.google.com/drive/folders/1BEqdToXQf_QLfxsGzzDk_xE1Dk31Bnow>)

```{r echo=FALSE}
tibble(
  Step = c("Datum Shift", 
           "Remove Invalid Ranges", 
           "Remove data",
           "Oscillations",
           "Oscillations",
           "Replace values"),
  Description = c(
    "Applied a 1.9 ft datum shift for Bell Hill Rd for December 2022",
    "Between 08/15/2022 and 12/07/2022 assign NA values to Bell Hill Rd. After 12/07/2022 and until depths drop to ~0 on 06/10/23, correct depths -1.9 ft. This depth is derived from transect taken on 1/24/2023",
    "Remove data between 04/05/2023 and 06/10/2023 for Bell Hill Gage. Also going to remove the data from 09/01/2023 to 09/27/2023 when the transducer was removed.",
    "Performed offset correction for dry oscillating conditions. Calculated average oscillation offsets for each transducer and applied vertical adjustments to center dry values around 0 ft of depth.",
    "Assign all values less than or equal to the maximum observed depth among these dry conditions oscillations for each transducer to zero",
    "Something odd is happening at Argonaut starting in August of 2023, lasting until the first rains of WY 2024 in December 2023. Sudden, high oscillation recordings while other gages show 0 flow, and precipitation record shows no precipitation. Replace values between the pattern starting (08/15/2023) and first real flows of WY 2024 (12/19/2023)."
  ),
  Affected_Data = c(
    "Bell Hill Rd", 
    "Bell Hill Rd", 
    "Bell Hill Rd",
    "All locations",
    "All locations",
    "Argonaut Rd"
  )
) |> knitr::kable(caption = "Summary of Adjustments Made to Surface Water Data")

```

#### Datum Shift

```{r}
# only look at data reported in the 2023 report (ends 11/13/23)
surface_water <- surface_water |> 
  filter(datetime <= '2023-11-13')

```

```{r}
surface_water <- surface_water |> 
  mutate(depth_adjust = 
           case_when(
             name == "Bell Hill Rd" & 
               datetime > as.POSIXct("2022-08-15 07:30:00", tz="America/Los_Angeles") & 
               datetime < as.POSIXct("2022-12-07 15:30:00", tz="America/Los_Angeles") ~ 
               0, #only way casewhen() will take NA value???
             name == "Bell Hill Rd" & 
               datetime > as.POSIXct("2022-12-07 7:45:00", tz="America/Los_Angeles") & 
               datetime < as.POSIXct("2023-06-10 15:00:00", tz="America/Los_Angeles") ~ 
               depth_ft - 1.9,
             T ~ depth_ft
           ))

ggplot(data = surface_water |> filter(name == "Bell Hill Rd"), aes(x = datetime, y = depth_adjust, color = name)) + 
  geom_line() + 
  theme_light() +
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%b '%y",
                   date_breaks = "2 months") +
  theme(axis.text.x = element_text(size = 7, angle = 45)) +
  labs(
    title = "QC - Bell Hill Rd with Datum Shift",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) 

```

Compare to Water Board data

```{r}
# From this we see that the datum shift makes our data match with Water Board's data at the same location for most of the winter. 
# However, they begin to diverge in early April of 2023. 
# 
# To account for this, going to remove data between 04/05/2023 and 06/10/2023 for Bell Hill Gage. 
# 
# Also going to remove the data from 09/01/2023 to 09/27/2023 when the transducer was removed. 

ggplot(data = surface_water |> filter(name == "Bell Hill Rd"), aes(x=datetime, y=depth_adjust, color = "BVR EPA")) + 
  geom_line() + 
  geom_line(data = SW_bellhill_WB, aes(x=Date, y = `Depth (ft)`, color = "Water Board")) + 
  scale_color_manual(name = "", values = c("BVR EPA" = "#1B9E77", "Water Board" = "red")) + 
  scale_y_continuous(limits = c(-1.75, 6.5), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "2 weeks",
                   minor_breaks = "1 week",
                   limits = c(as.POSIXct("2023-02-15 00:00:00", tz="America/Los_Angeles"), as.POSIXct("2023-07-01 00:00:00", tz="America/Los_Angeles"))
  ) + 
  labs(x = "Date", y = "Depth (ft)", title = "Comparison of BVR EPA and Water Board Transducer \n  Measurements at Bell Hill Rd, 2023") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

```

```{r}
surface_water <- surface_water |> 
  mutate(depth_adjust02 = 
           case_when(
             name == "Bell Hill Rd" & 
               datetime > as.POSIXct("2023-04-05 08:00:00", tz="America/Los_Angeles") &
               datetime < as.POSIXct("2023-06-10 15:00:00", tz="America/Los_Angeles") ~
               NA_real_,
             name == "Bell Hill Rd" & 
               datetime >= as.POSIXct("2023-09-01 08:00:00", tz="America/Los_Angeles") &
               datetime < as.POSIXct("2023-09-27 09:00:00", tz="America/Los_Angeles") ~ 
               0,
             T ~ depth_adjust
           ))

ggplot(data = surface_water |> filter(name == "Bell Hill Rd"), aes(x = datetime, y = depth_adjust02, color = name)) + 
  geom_line() + 
  theme_light() +
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%b '%y",
                   date_breaks = "2 months") +
  theme(axis.text.x = element_text(size = 7, angle = 45)) +
  labs(
    title = "QC - adjustments from waterboard comparison",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) 

```

#### Vertical Oscillations

This resolves issues with oscillations when the creeks are dry. Each
dataset is vertically transformed to get the zero flow values to roughly
evenly distribute around 0 feet depth. Assign all values less than or
equal to the maximum observed depth among these dry conditions
oscillations for each transducer to zero.

```{r}
bellhill_offset <- mean((surface_water |> filter(name == "Bell Hill Rd"))$depth_adjust02[(surface_water |> filter(name == "Bell Hill Rd"))$depth_adjust02 <= 0.01], na.rm = T)

argonaut_offset <- mean((surface_water |> filter(name == "Argonaut Rd"))$depth_adjust02[(surface_water |> filter(name == "Argonaut Rd"))$depth_adjust02 <= 0.062], na.rm = T)

sodabay_offset <- mean((surface_water |> filter(name == "Soda Bay Rd"))$depth_adjust02[(surface_water |> filter(name == "Soda Bay Rd"))$depth_adjust02 <= 0.087], na.rm = T)

adoberes_offset <- mean((surface_water |> filter(name == "Adobe Reservoir"))$depth_adjust02[(surface_water |> filter(name == "Adobe Reservoir"))$depth_adjust02 <= 0.059], na.rm = T)

highlandspringsres_offset <- mean((surface_water |> filter(name == "Highland Springs Reservoir"))$depth_adjust02[(surface_water |> filter(name == "Highland Springs Reservoir"))$depth_adjust02 <= -0.086], na.rm = T)
```

```{r}
surface_water <- surface_water |> 
  mutate(depth_adjust03 = case_when(
    # The following numbers are derived from the maximum "zero flow" values across whole record for each transducer
    name == "Bell Hill Rd" ~ depth_adjust02 - bellhill_offset,
    name == "Argonaut Rd" ~ depth_adjust02 - argonaut_offset,
    name == "Soda Bay Rd" ~ depth_adjust02 - sodabay_offset,
    # Following values are based on an offset that will make the lowest oscillations oscillate around zero.
    name == "Adobe Reservoir" ~ depth_adjust02 - adoberes_offset,
    name == "Highland Springs Reservoir" ~ depth_adjust02 - highlandspringsres_offset,
    T ~ depth_adjust02
  )) |> 
  mutate(
    depth_adjust03 = case_when(
      name == "Bell Hill Rd" & depth_adjust03 <= 0.0759 ~ 0,
      name == "Argonaut Rd" & depth_adjust03 < 0.0768 ~ 0,
      name == "Soda Bay Rd" & depth_adjust03 <= 0.0753 ~ 0,
      name == "Adobe Reservoir" & depth_adjust03 <= 0.063 ~ 0,
      name == "Highland Springs Reservoir" & depth_adjust03 <= 0.048 ~0,
      T ~ depth_adjust03
    )) 

ggplot(data = surface_water, aes(x = datetime, y = depth_adjust03, color = name)) + 
  geom_line() + 
  theme_light() +
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%b '%y",
                   date_breaks = "2 months") +
  theme(axis.text.x = element_text(size = 7, angle = 45)) +
  labs(
    title = "QC - Vertical Oscillation Adjustments",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) 

```

```{r}
# Something odd is happening at Argonaut starting in August of 2023, lasting until the first rains of WY 2024 in December 2023. Sudden, high oscillation recordings while other gages show 0 flow, and precipitation record shows no precipitation. Let's replace values between the pattern starting (08/15/2023) and first real flows of WY 2024 (12/19/2023). 
# 
surface_water <- surface_water |> 
  mutate(depth_adjust04 = 
           case_when(
             name == "Argonaut Rd" & 
               datetime > as.POSIXct("2023-08-16 00:00:00", tz="America/Los_Angeles") &
               datetime < as.POSIXct("2023-12-19 09:15:00", tz="America/Los_Angeles") ~ 
               0,
             T ~ depth_adjust03
           ))

ggplot(data = surface_water |> filter(name == "Argonaut Rd"), aes(x=datetime, y=depth_adjust04, color=name)) + 
  geom_line() + 
  theme_light() +
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%b '%y",
                   date_breaks = "2 months") +
  theme(axis.text.x = element_text(size = 7, angle = 45)) +
  labs(
    title = "QC - Update to Argonaut Rd",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) 
```

### NEW 2024 DATA QC

**Description of New Data** - new data was uploaded for `2024-09-06`

**Description of QC**

-   Zero flow oscillations were similar in the new 2024 data from Adobe
    Reservoir, Highland Springs Reservoir, and Soda Bay Road. For these
    sites, we will calculate a new zero flow vertical offset for all the
    data.
-   Bell Hill Rd
-   Argonaut Rd: used the same methodology as previous analysis to perform the offset 

```{r}
# this is all the new data: 
new_surface_water <- readRDS(here::here('data', 'surface_water', 'surface_water_data_aggregated.RDS')) |> 
  filter(datetime > '2023-11-13')

```

```{r}
# this pulls the new and some of the older data to do manual QC
new_data <- c(
  'Adobe Reservoir Outlet_Append_2024-09-06_12-37-57-838-BaroMerge.csv',
  'Argonaut_Append_2024-09-06_13-25-29-804-BaroMerge.csv',
  'Bell Hill_Append_2024-09-06_12-58-21-777-BaroMerge.csv',
  'Highland Springs Outlet_Append_2024-09-06_13-09-48-628-BaroMerge.csv',
  'Soda Bay_Append_2024-09-06_11-46-00-928-BaroMerge.csv'
)

# Extract the iteration(s) corresponding to the new data
new_data_iterations <- surface_water |> 
  filter(file_name %in% new_data) |> 
  pull(iteration) |> 
  unique()

# Get the previous iteration(s)
previous_iterations <- new_data_iterations - 2

# Combine the new data with the corresponding previous data
new_data_and_previous_data <- surface_water |> 
  filter(iteration >= previous_iterations) 

# plot
ggplot(new_data_and_previous_data, aes(datetime, y = depth_ft)) +
  geom_line(aes(color = as.factor(iteration))) +
  theme_minimal() +
  facet_wrap(~name, ncol = 2) + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom")


```

#### Adobe Reservoir

-   zero flow oscillations look similar between the older and newer data
-   **QC performed:** Calculate a new offset based on all the data

```{r}
adobe <- new_surface_water |> 
  filter(name == "Adobe Reservoir") |> 
  ggplot(aes(datetime, y = depth_ft)) +
  geom_line() +
  theme_minimal() +
  facet_wrap(~name, ncol = 2) + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom") 

ggplotly(adobe)

```

#### Highland Springs Reservoir

-   large spikes are from reservoir releases

-   zero flow oscillations look similar between the older and newer data

-   **QC performed:** Calculate a new offset based on all the data

```{r}
highland <- new_data_and_previous_data |> 
  filter(name == "Highland Springs Reservoir") |> 
  ggplot(aes(datetime, y = depth_ft)) +
  geom_line(aes(color = as.factor(iteration))) +
  theme_minimal() +
  facet_wrap(~name, ncol = 2) + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom") 

ggplotly(highland)

```

#### Soda Bay Rd

-   zero flow oscillations look similar between the older and newer data

-   **QC performed:** Calculate a new offset based on all the data

```{r}
soda <- new_data_and_previous_data |> 
  filter(name == "Soda Bay Rd") |> 
  ggplot(aes(datetime, y = depth_ft)) +
  geom_line(aes(color = as.factor(iteration))) +
  theme_minimal() +
  facet_wrap(~name, ncol = 2) + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom") 

ggplotly(soda)

```

#### Bell Hill Rd

-   Reservoir releases from 7-19 are likely the result of the spike around 7-22    

-   **QC performed:**: The updated data had similar zero flow oscillations so we used the entire data series to calculate the vertical transformation. 


```{r}
bell <- new_data_and_previous_data |> 
  filter(name == "Bell Hill Rd") |> 
  ggplot(aes(datetime, y = depth_ft)) +
  geom_line(aes(color = as.factor(iteration))) +
  theme_minimal() +
  facet_wrap(~name, ncol = 2) + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom") 

ggplotly(bell)

```

#### Argonaut Rd

-   high oscillations in low flow; evident where it goes from bad
    oscillation data to good measurements.

-   **QC performed:** Cut out high oscillation during low flow and make
    it zero and use prior season vertical transformations

```{r}
arg <- surface_water |> 
  filter(name == "Argonaut Rd") |> 
  ggplot(aes(datetime, y = depth_ft)) +
  geom_line(aes(color = as.factor(iteration))) +
  theme_minimal() +
  facet_wrap(~name, ncol = 2) + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom") 

ggplotly(arg)

```

### Peform QC on sites

```{r}
# all data 
surface_water <- readRDS(here::here('data', 'surface_water', 'surface_water_data_aggregated.RDS')) 
```

```{r}
# consistent with what was done with previous data after comparing to waterboard 2023 data 
surface_water <- surface_water |> 
  mutate(depth_adjust = 
           case_when(
             name == "Bell Hill Rd" & 
               datetime > as.POSIXct("2022-08-15 07:30:00", tz="America/Los_Angeles") & 
               datetime < as.POSIXct("2022-12-07 15:30:00", tz="America/Los_Angeles") ~ 
               0, #only way casewhen() will take NA value???
             name == "Bell Hill Rd" & 
               datetime > as.POSIXct("2022-12-07 7:45:00", tz="America/Los_Angeles") & 
               datetime < as.POSIXct("2023-06-10 15:00:00", tz="America/Los_Angeles") ~ 
               depth_ft - 1.9,
             T ~ depth_ft
           ))

surface_water <- surface_water |> 
  mutate(depth_adjust02 = 
           case_when(
             name == "Bell Hill Rd" & 
               datetime > as.POSIXct("2023-04-05 08:00:00", tz="America/Los_Angeles") &
               datetime < as.POSIXct("2023-06-10 15:00:00", tz="America/Los_Angeles") ~
               NA_real_,
             name == "Bell Hill Rd" & 
               datetime >= as.POSIXct("2023-09-01 08:00:00", tz="America/Los_Angeles") &
               datetime < as.POSIXct("2023-09-27 09:00:00", tz="America/Los_Angeles") ~ 
               0,
             T ~ depth_adjust
           ))

```

#### Calculate new offsets 

```{r eval=FALSE, include=FALSE}
# trying a new way of calculating offsets 
offsets <- surface_water |> 
  group_by(name) |> 
  filter(depth_adjust02 <= 0) |> 
  summarise(mean = mean(depth_adjust02, na.rm = T))

```

```{r}
# TODO: where do these hardcoded values come from? 
# The maximum values that are considered to be zero flow
# TODO: look at each transducer, look at time periods where zero flow conditions exist and take the mean to get away from hardcoded values 
bellhill_offset_updated <- mean((surface_water |> filter(name == "Bell Hill Rd"))$depth_adjust02[(surface_water |> filter(name == "Bell Hill Rd"))$depth_adjust02 <= 0.01], na.rm = T)

argonaut_offset_updated <- mean((surface_water |> filter(name == "Argonaut Rd"))$depth_adjust02[(surface_water |> filter(name == "Argonaut Rd"))$depth_adjust02 <= 0.062], na.rm = T)

sodabay_offset_updated <- mean((surface_water |> filter(name == "Soda Bay Rd"))$depth_adjust02[(surface_water |> filter(name == "Soda Bay Rd"))$depth_adjust02 <= 0.087], na.rm = T)

adoberes_offset_updated <- mean((surface_water |> filter(name == "Adobe Reservoir"))$depth_adjust02[(surface_water |> filter(name == "Adobe Reservoir"))$depth_adjust02 <= 0.059], na.rm = T)

highlandspringsres_offset_updated <- mean((surface_water |> filter(name == "Highland Springs Reservoir"))$depth_adjust02[(surface_water |> filter(name == "Highland Springs Reservoir"))$depth_adjust02 <= -0.086], na.rm = T)
```

Compare offsets

| Site                       | Old Offset                    | New Offset                            |
|------------------------|------------------------|------------------------|
| Bell Hill                  | `r bellhill_offset`   | `r bellhill_offset_updated`           |
| Argonaut                   | `r argonaut_offset`   | `r argonaut_offset_updated`           |
| Soda Bay                   | `r sodabay_offset`    | `r sodabay_offset_updated`            |
| Adobe Reservoir            | `r adoberes_offset`   | `r adoberes_offset_updated`           |
| Highland Springs Reservoir | `r highlandspringsres_offset` | `r highlandspringsres_offset_updated` |

```{r}
surface_water <- surface_water |> 
  mutate(depth_adjust03 = case_when(
    # The following numbers are derived from the maximum "zero flow" values across whole record for each transducer
    name == "Bell Hill Rd" ~ depth_adjust02 - bellhill_offset_updated,
    name == "Argonaut Rd" ~ depth_adjust02 - argonaut_offset_updated,
    name == "Soda Bay Rd" ~ depth_adjust02 - sodabay_offset_updated,
    # Following values are based on an offset that will make the lowest oscillations oscillate around zero.
    name == "Adobe Reservoir" ~ depth_adjust02 - adoberes_offset_updated,
    name == "Highland Springs Reservoir" ~ depth_adjust02 - highlandspringsres_offset_updated,
    T ~ depth_adjust02
  )) |> 
  mutate(
    depth_adjust03 = case_when(
      name == "Bell Hill Rd" & depth_adjust03 <= 0.0759 ~ 0,
      name == "Argonaut Rd" & depth_adjust03 < 0.0768 ~ 0,
      name == "Soda Bay Rd" & depth_adjust03 <= 0.0753 ~ 0,
      name == "Adobe Reservoir" & depth_adjust03 <= 0.063 ~ 0,
      name == "Highland Springs Reservoir" & depth_adjust03 <= 0.048 ~0,
      T ~ depth_adjust03
    )) 

surface_water <- surface_water |> 
  mutate(depth_adjust04 = 
           case_when(
             name == "Argonaut Rd" & 
               datetime > as.POSIXct("2023-08-16 00:00:00", tz="America/Los_Angeles") &
               datetime < as.POSIXct("2023-12-19 09:15:00", tz="America/Los_Angeles") ~ 
               0,
             T ~ depth_adjust03
           ))
```


```{r eval=FALSE, include=FALSE}
# THIS IS A TEST to see how automated offsets impacted results 
surface_water <- surface_water |> 
  mutate(depth_adjust03 = case_when(
    # The following numbers are derived from the maximum "zero flow" values across whole record for each transducer
    name == "Bell Hill Rd" ~ depth_adjust02 - offsets[offsets$name == "Bell Hill Rd", ]$mean,
    name == "Argonaut Rd" ~ depth_adjust02 - offsets[offsets$name == "Argonaut Rd", ]$mean,
    name == "Soda Bay Rd" ~ depth_adjust02 - offsets[offsets$name == "Soda Bay Rd", ]$mean,
    # Following values are based on an offset that will make the lowest oscillations oscillate around zero.
    name == "Adobe Reservoir" ~ depth_adjust02 - offsets[offsets$name == "Adobe Reservoir", ]$mean,
    name == "Highland Springs Reservoir" ~ depth_adjust02 - offsets[offsets$name == "Highland Springs Reservoir", ]$mean,
    T ~ depth_adjust02
  )) 

# Now look at where there data is hovering around zero 
vals_to_zero <- surface_water |> 
  group_by(name) |> 
  filter(depth_adjust03 < 0.5) |> 
  slice_max(order_by = depth_adjust03, prop = 0.99) |> 
  summarise(mean = mean(depth_adjust03))

# scanned the data again and decided the max value seen in the vertically transformed data?
# I instead used the mean of the 99th percentile 
 surface_water <- surface_water |> 
   mutate(
    depth_adjust03 = case_when(
      name == "Bell Hill Rd" & depth_adjust03 <= vals_to_zero[vals_to_zero$name == "Bell Hill Rd", ]$mean ~ 0,
      name == "Argonaut Rd" & depth_adjust03 < vals_to_zero[vals_to_zero$name == "Argonaut Rd", ]$mean ~ 0,
      name == "Soda Bay Rd" & depth_adjust03 <= vals_to_zero[vals_to_zero$name == "Soda Bay Rd", ]$mean ~ 0,
      name == "Adobe Reservoir" & depth_adjust03 <= vals_to_zero[vals_to_zero$name == "Adobe Reservoir", ]$mean ~ 0,
      name == "Highland Springs Reservoir" & depth_adjust03 <= vals_to_zero[vals_to_zero$name == "Highland Springs Reservoir", ]$mean ~ 0,
      T ~ depth_adjust03
    )) 

surface_water <- surface_water |> 
  mutate(depth_adjust04 = 
           case_when(
             name == "Argonaut Rd" & 
               datetime > as.POSIXct("2023-08-16 00:00:00", tz="America/Los_Angeles") &
               datetime < as.POSIXct("2023-12-19 09:15:00", tz="America/Los_Angeles") ~ 
               0,
             T ~ depth_adjust03
           ))
```


#### Plot QC'd sites

```{r}
all_sites_with_qc <- surface_water |> 
  ggplot() +
  geom_line(aes(datetime, y = depth_adjust04, color = "post-QC")) +
    geom_line(aes(datetime, y = depth_ft, color = "pre-QC")) +
  theme_minimal() +
  facet_wrap(~name, ncol = 2) + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom") 

ggplotly(all_sites_with_qc)
#all_sites_with_qc
```

```{r}
all_sites_qc <- surface_water |> 
  ggplot(aes(datetime, y = depth_adjust04)) +
  geom_line() +
  theme_minimal() +
  facet_wrap(~name, ncol = 2) + 
  ylab("Depth (ft)") +
  xlab("Date") + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom") 

#ggsave(filename = 'all_sites_qcd.png', here::here("analysis", "surface_water", "2024_figs", "all_sites_qcd.png"))

#ggplotly(all_sites_qc)
#all_sites_qc
```

#### Compare to 2024 waterboard data for Bell Hill Rd

**Note**
-   BV EPA data is reporting a consistently larger depth when compared to the Water Board 2024 data 
-   Not modifying BV EPA data because this doesn't necessarily indicate an issue with the datum or other

```{r}
ac4_plot <- ggplot(data = surface_water |> filter(name == "Bell Hill Rd"), aes(x=datetime, y=depth_adjust04, color = "BVR EPA")) + 
  geom_line() + 
  geom_line(data = SW_bellhill_WB, aes(x=Date, y = `Depth (ft)`, color = "Water Board")) + 
  geom_line(data = adobe_ac4_2024, aes(x = date_time, y = depth_ft, color = "Water Board 2024")) +
  scale_color_manual(name = "", values = c("BVR EPA" = "#1B9E77", "Water Board" = "darkred", "Water Board 2024" = "darkblue")) + 
  #scale_y_continuous(limits = c(-1.75, 6.5), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "2 weeks",
                   minor_breaks = "1 week",
                   limits = c(as.POSIXct("2023-02-15 00:00:00", tz="America/Los_Angeles"), as.POSIXct("2024-12-31 00:00:00", tz="America/Los_Angeles"))
  ) + 
  labs(x = "Date", y = "Depth (ft)", title = "Comparison of BVR EPA and Water Board Transducer \n  Measurements at Bell Hill Rd, 2023 + 2024") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

ggplotly(ac4_plot)

```

#### Compare Soda Bay Rd

-   Depth comparisons mostly align except for the zero flow where DWR reports lower elevations; reason could be explained by the DWR transducer being at a slightly lower bed elevation
-   This particular location has a lot of variability in the bed elevation
<!-- -   Depth isn't necessarily the best way to compare the two because the transducers could be at different depths in the channel; better way would be compare WSE  -->
<!-- -   WSE BVEPA: 1329.229 - BV EPA WSE (this number is 6 years old, could it have moved?) -->
<!-- -   WSE CDEC ACF: 1300 -->
<!-- -    -->

```{r}
ggplot(data = surface_water |> 
         filter(name == "Soda Bay Rd") , 
       aes(x=datetime, y=depth_adjust04, color = "BVR EPA")) + 
  geom_line() + 
  geom_line(data = acf_depth_adj, aes(x=datetime, y = depth_ft, color = "ACF (DWR)")) + 
 # geom_line(data = acf_depth_adj, aes(x=datetime, y = parameter_value, color = "ACF (DWR) - uncorrected")) + 
  scale_color_manual(name = "", values = c("BVR EPA" = "#1B9E77", "ACF (DWR)" = "darkred")) + 
  #scale_y_continuous(limits = c(-1.75, 6.5), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "2 weeks",
                   minor_breaks = "1 week",
                   limits = c(as.POSIXct("2024-01-01 00:00:00", tz="America/Los_Angeles"), as.POSIXct("2024-12-31 00:00:00", tz="America/Los_Angeles"))
  ) + 
  labs(x = "Date", y = "Depth (ft)", title = "Comparison of BVR EPA and DWR (ACF) \n  Measurements at Soda Bay Rd") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))


```

```{r}
saveRDS(surface_water, here::here("data", "surface_water", "cleaned_surface_water.RDS"))

surface_water <- readRDS(here::here("data", "surface_water", "cleaned_surface_water.RDS"))

# sent to Big Valley on 4/29
surface_water |> 
  select(name, datetime, pressure_psi, temperature_f, depth_ft_raw = depth_ft, depth_ft_qc = depth_adjust04) |> 
  write_csv(here::here("data", "surface_water", "cleaned_surface_water_data_052025.csv"))

```

```{r}
knitr::knit_exit()
```

### Data Exploration

#### Smoothed Data (Moving Average)

The data looks clean, but the sharp peaks make it more difficult to
ascertain trends on a longer time interval. To remedy this, we will
apply a 7 day moving average to the data.

TODO: 
-   create one image with three stream gauges 
-   create one for the two reservoir sites

```{r}
surface_water <- surface_water |> 
  group_by(name) |> 
  mutate(
    depth_07dMA = zoo::rollmean(depth_adjust04, 672, fill=NA),
    depth_01dMA = zoo::rollmean(depth_adjust04, 96, fill=NA)
  )

ggplot(data = surface_water, aes(x = datetime, y = depth_07dMA, color = name)) + 
  geom_line() + 
  theme_light() +
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%b '%y",
                   date_breaks = "2 months") +
  theme(axis.text.x = element_text(size = 7, angle = 45)) +
  labs(
    title = "7-Day Moving Average Stage",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  )

ggplot(data = surface_water, aes(x = datetime, y = depth_01dMA, color = name)) + 
  geom_line() + 
  theme_light() +
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%b '%y",
                   date_breaks = "2 months") +
  theme(axis.text.x = element_text(size = 7, angle = 45)) +
  labs(
    title = "1-Day (24 hour) Moving Average Stage",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  )
```

```{r}
#save output
AdobeCreekTransducers_BVR_Depth_Cleaned <- surface_water |> 
  mutate(
    PT_id = case_when(
      name == "Bell Hill Rd" ~ "AdobePT03_BVR",
      name == "Argonaut Rd" ~ "AdobePT02_BVR",
      name == "Soda Bay Rd" ~ "AdobePT01_BVR",
      name == "Adobe Reservoir" ~ "AdobePT05_BVR",
      name == "Highland Springs Reservoir" ~ "AdobePT04_BVR"
    )
  ) |> 
  select(-c(depth_adjust, depth_adjust02, depth_adjust03)) %>%
  rename(depth_ft_raw = depth_ft,
         depth_ft_cleaned = depth_adjust04,
         depth_07dayMovingAvg = depth_07dMA,
         depth_01dayMovingAvg = depth_01dMA,
         datetime_UTC = datetime)

write_csv(AdobeCreekTransducers_BVR_Depth_Cleaned, here::here('data', 'surface_water', 'cleaned_deliverable','AdobeCreekTransducers_BVR_Depth_Cleaned.csv'))

```

This 7-day moving average makes trends on a week time interval clearer
and also better illustrates trends between the monitoring locations. To
further interrogate relationships between monitoring locations, we take
a look at mean monthly stages across the sites. TODO - does this
happen??

#### Water Surface Elevations

TODO: 
-   include in report 

```{r}
sw_wse <- surface_water |> 
  mutate(
    # estimated elevation of each of the sensors - could have changed slightly but good enough for the figure 
    sensor_elev = case_when(
      name == "Argonaut Rd" ~ 1350.318,
      name == "Soda Bay Rd" ~ 1329.229,
      name == "Adobe Reservoir" ~ 1420.6,
      name == "Highland Springs Reservoir" ~ 1422.9,
      T ~ 1402.281
    ),
    WSE = sensor_elev + depth_adjust04,
    WSE_7dMA = sensor_elev + depth_07dMA,
    WSE_1dMA = sensor_elev + depth_01dMA
  )

saveRDS(sw_wse, here::here("data", "surface_water", "sw_wse_2024.RDS"))

ggplot(data = sw_wse, aes(x = datetime, y = WSE, color = name)) + 
  geom_line() + 
  theme_light() +
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%b '%y",
                   date_breaks = "2 months") +
  theme(axis.text.x = element_text(size = 7, angle = 45)) +
  labs(
    title = "Water Surface Elevations",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  )

```

#### Monthly Average Summary

This graphic allows us to interrogate the relationships between stages
at the 3 monitoring locations during the most important months for chi
spawning.

TODO: 
-   Helpful to include since it shows where flows are at their peak and by month stage relationship; interesting that Bell Hill, though farther upstream has a higher mean stage whereas it has a smaller peak flow 
```{r}
spawning_months <- surface_water |> 
  filter(name %in% c("Bell Hill Rd", "Argonaut Rd", "Soda Bay Rd")) |> 
  mutate(
    month = format(datetime, "%m"),
    year = format(datetime, "%Y"),
    WY = ifelse(month %in% c("10","11","12"), as.numeric(year)+1, as.numeric(year))
  ) |> 
  mutate(month = factor(format(datetime, "%b"), levels = c("Oct", "Nov", "Dec","Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")),
        name = factor(name, levels = c("Bell Hill Rd", "Argonaut Rd", "Soda Bay Rd"))) |> 
  group_by(name, month) |> 
  summarize(
    mean = mean(depth_adjust04, na.rm = T)
  ) |> 
  ungroup()

ggplot(spawning_months, aes(x = month, y = mean, fill = name)) + 
  geom_col(position = "dodge") + 
  theme_light() +
  scale_fill_brewer(type = 'qual', palette = 'Dark2') +
  labs(x = "Month", y = "Mean Stage on Adobe Creek", fill = "Gage Location", title = "Mean Monthly Stage at 3 Adobe Creek Stage Gaging Sites \n2019-2024")

```

**Wetter years clearly have a different pattern**

```{r}
spawning_months_by_WY <- surface_water |> 
  filter(name %in% c("Bell Hill Rd", "Argonaut Rd", "Soda Bay Rd")) |> 
  mutate(
    month = format(datetime, "%m"),
    year = format(datetime, "%Y"),
    WY = ifelse(month %in% c("10","11","12"), as.numeric(year)+1, as.numeric(year))
  ) |> 
  mutate(month = factor(format(datetime, "%b"), levels = c("Oct", "Nov", "Dec","Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")),
        name = factor(name, levels = c("Bell Hill Rd", "Argonaut Rd", "Soda Bay Rd"))) |> 
  group_by(WY, name, month) |> 
  summarize(
    mean = mean(depth_adjust04, na.rm = T)
  ) |> 
  ungroup() |> 
  filter(!is.na(name))
```

```{r}
ggplot(spawning_months_by_WY |> filter(WY == 2019), aes(x=month, y=mean, fill=name)) + 
  geom_col(position = "dodge") + 
  theme_light() +
  scale_fill_brewer(type = 'qual', palette = 'Dark2') +
  labs(x = "Month", y = "Average Depth (ft)", fill = "Gage Location", title = "2019") + 
  ylim(c(0,4.5))+ 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        axis.title.x = element_blank(),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "none",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

ggplot(spawning_months_by_WY |> filter(WY == 2020), aes(x=month, y=mean, fill=name)) + 
  geom_col(position = "dodge") + 
  theme_light() +
  scale_fill_brewer(type = 'qual', palette = 'Dark2') +
  labs(x = "Month", y = "Average Depth (ft)", fill = "Gage Location", title = "2020") + 
  ylim(c(0,4.5))+ 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        axis.title.x = element_blank(),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "none",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

ggplot(spawning_months_by_WY |> filter(WY == 2021), aes(x=month, y=mean, fill=name)) + 
  geom_col(position = "dodge") + 
  theme_light() +
  scale_fill_brewer(type = 'qual', palette = 'Dark2') +
  labs(x = "Month", y = "Average Depth (ft)", fill = "Gage Location", title = "2021") + 
  ylim(c(0,4.5))+ 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        axis.title.x = element_blank(),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "none",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

ggplot(spawning_months_by_WY |> filter(WY == 2022), aes(x=month, y=mean, fill=name)) + 
  geom_col(position = "dodge") + 
  theme_light() +
  scale_fill_brewer(type = 'qual', palette = 'Dark2') +
  labs(x = "Month", y = "Average Depth (ft)", fill = "Gage Location", title = "2022") + 
  ylim(c(0,4.5))+ 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        axis.title.x = element_blank(),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "none",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

ggplot(spawning_months_by_WY |> filter(WY == 2023), aes(x=month, y=mean, fill=name)) + 
  geom_col(position = "dodge") + 
  scale_fill_brewer(type = 'qual', palette = 'Dark2') +
  labs(x = "Month", y = "Average Depth (ft)", fill = "Gage Location", title = "2023") + 
  ylim(c(0,4.5))+ 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        axis.title.x = element_blank(),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "none",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

# TODO: add for 2024
```

#### Flow-Stage Plot Generation

A bit of a stand-in for a rating curve. Just plotting our flow
measurements with stages reported from the transducer in these
locations.

**Don't include in updated report**

```{r}
stage_vs_flow <- stage_flow |> select(c("Site_Name", "Date", "Time", "Flow_cfs", "Corrected_Depth_ft", "WSE_ft-NAVD88"))|> 
  mutate(Date = as.Date(Date, format = "%m.%d.%Y"))
```

```{r}
p_bellhill <- ggplot(stage_vs_flow |> filter(Site_Name == "Bell Hill Rd"), aes(y = Corrected_Depth_ft, x = Flow_cfs)) + 
  geom_point(size=2) + 
  labs(x = "Flow (cfs)", y="Depth (ft)", title="Flow v Depth at Bell Hill Road") + 
  scale_y_continuous(limits = c(0,4),
                     breaks = seq(0,4,0.5),
                     minor_breaks = seq(-0.25,4,0.25)) +
  scale_x_continuous(limits = c(0, 350),
                     breaks = seq(0,350,100),
                     minor_breaks = seq(0,350,25)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_arg <- ggplot(stage_vs_flow |> filter(Site_Name == "Argonaut Rd"), aes(y=Corrected_Depth_ft, x=Flow_cfs)) +  
  geom_point(size=2) +
  labs(x = "Flow (cfs)", y="Depth (ft)", title="Flow v Depth at Argonaut Road") + 
  scale_y_continuous(limits = c(0,2.5),
                     breaks = seq(0,2.5,0.5),
                     minor_breaks = seq(0,2.5,0.25)) +
  scale_x_continuous(limits = c(0, 100),
                     breaks = seq(0,100,50),
                     minor_breaks = seq(0,100,10)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_sodabay <- ggplot(stage_vs_flow |> filter(Site_Name == "Soda Bay Rd"), aes(y=Corrected_Depth_ft, x=Flow_cfs)) +  
  geom_point(size=2) + 
  labs(x = "Flow (cfs)", y="Depth (ft)", title="Flow v Depth at Soda Bay Road") + 
  scale_y_continuous(limits = c(0,2),
                     breaks = seq(0,2,0.5),
                     minor_breaks = seq(0,2,0.25)) +
  scale_x_continuous(limits = c(0, 100),
                     breaks = seq(0,100,50),
                     minor_breaks = seq(0,100,10)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_bellhill
p_arg
p_sodabay
```

### Data Quality Figures

Highlighting inherent noise and uncertainty

```{r}
p_base_noise <- ggplot(data = surface_water |> filter(name == "Bell Hill Rd"), aes(x=datetime, y=depth_adjust04, color=name)) + 
  geom_line() + 
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "3 days",
                   minor_breaks = "1 day",
                   limits = c(as.POSIXct("2019-04-14 0:00:00", tz="America/Los_Angeles"), as.POSIXct("2019-05-07 0:00:00", tz="America/Los_Angeles"))) +
  scale_y_continuous(limits = c(1.75,2.45),
                     breaks = c(1.8,2,2.2,2.4)) +
  # theme(axis.text.x = element_text(size = 10, angle = 45),
  #       legend.position = "none") +
  labs(
    title = "Approximately Daily Oscillation Patterns Following A Storm \nAdobe Creek at Bell Hill Rd, 2019",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) + 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "none",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_base_noise
```

This pattern seems to occur when depth levels off, such as following a
storm. Intensified oscillations in 2023 season on Bell Hill.

```{r}
p_worse_noise <- ggplot(data = surface_water |> filter(name == "Bell Hill Rd"), aes(x=datetime, y=depth_adjust04, color=name)) + 
  geom_line() + 
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "3 days",
                   minor_breaks = "1 day",
                   limits = c(as.POSIXct("2023-01-17 0:00:00", tz="America/Los_Angeles"), as.POSIXct("2023-02-06 0:00:00", tz="America/Los_Angeles"))) +
  scale_y_continuous(limits = c(1,3),
                     breaks = c(1,1.5,2,2.5,3)) +
  labs(
    title = "Approximately Daily Oscillation Patterns Following A Storm \nAdobe Creek at Bell Hill Rd, 2023",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "none",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_worse_noise
```

We can see that this oscillation is much worse in 2023. Some
oscillations are almost 0.5 feet! This is not a real physical
phenomenon.

Zero water depth oscillations

```{r}
p_zeroflow_noise <- ggplot(data = surface_water |> filter(name %in% c("Bell Hill Rd", "Argonaut Rd", "Soda Bay Rd")), aes(x=datetime, y=depth_adjust02, color=name)) + 
  geom_line() + 
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "3 days",
                   minor_breaks = "1 day",
                   limits = c(as.POSIXct("2021-07-01 0:00:00", tz="America/Los_Angeles"), as.POSIXct("2021-07-24 0:00:00", tz="America/Los_Angeles"))) +
  scale_y_continuous(limits = c(-0.25,0.25)) +
  labs(
    title = "Approximately Daily Oscillations at Zero Flow, 2021",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) + 
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_zeroflow_noise
```

**Argonaut Error in 2023**

```{r}
p_argonaut_error <- ggplot(data = surface_water|> filter(name == "Argonaut Rd"), aes(x=datetime, y=depth_adjust02, color="Argonaut")) + 
  geom_line() + 
  geom_line(data = surface_water|> filter(name == "Soda Bay Rd"), aes(color="Soda Bay")) +
  scale_color_manual(name = "", values = c("Argonaut" = "#D95F02", "Soda Bay" = "#7570B3")) + 
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "1 week",
                   minor_breaks = "1 day",
                   limits = c(as.POSIXct("2023-08-01 0:00:00", tz="America/Los_Angeles"), as.POSIXct("2023-10-16 0:00:00", tz="America/Los_Angeles"))) +
  scale_y_continuous(limits = c(-0.25,2),
                     breaks = c(0, 0.5, 1, 1.5, 2)) +
  labs(
    title = "Erroneuous Oscillating Singal at Argonaut Road, 2023 \nSoda Bay Depths Included as Downstream Reference",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_argonaut_error
```

**Bell Hill Sudden Datum Shift**

```{r}
p_bellhill_datumshift <- ggplot(data = surface_water |> filter(name == "Bell Hill Rd"), aes(x=datetime, y=depth_ft, color=name)) + 
  geom_line() + 
  scale_color_brewer(type = 'qual', palette = 'Dark2') +
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "2 weeks",
                   minor_breaks = "1 week",
                   limits = c(as.POSIXct("2022-07-24 0:00:00", tz="America/Los_Angeles"), as.POSIXct("2022-11-01 0:00:00", tz="America/Los_Angeles"))) +
  scale_y_continuous(limits = c(-0.5,2),
                     breaks = c(0,1,2)) +
  labs(
    title = "Sudden Datum Shift at Bell Hill Rd, Late 2022",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 0, vjust = 0),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "none",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_bellhill_datumshift
```

### Reservoir Figures

```{r}
p_reservoir_data <- ggplot(data = surface_water |> filter(name == "Adobe Reservoir"), aes(x=datetime, y=depth_adjust04, color= "Adobe Reservoir")) + 
  geom_line() + 
  geom_line(data = surface_water |> filter(name == "Highland Springs Reservoir"), aes(x=datetime, y=depth_adjust04, color= "Highland Springs Reservoir")) + 
  scale_color_manual(name = "", values = c("Adobe Reservoir" = "#e7298a", "Highland Springs Reservoir" = "#66a61e")) + 
  scale_x_datetime(date_labels = "%m/%d",
                   date_breaks = "2 weeks",
                   minor_breaks = "1 week",
                   limits = c(as.POSIXct("2023-05-01 0:00:00", tz="America/Los_Angeles"), as.POSIXct("2023-10-30 0:00:00", tz="America/Los_Angeles"))) +
  # scale_y_continuous(limits = c(-0.5,2),
  #                    breaks = c(0,1,2)) +
  labs(
    title = "Reservoir Transducer Data, 2023",
    y = "Depth (ft)",
    color = "Gage Location",
    x = "Date"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 45, vjust = 0.5),
        panel.grid.major = element_line(colour = "grey60", size = 0.25),
        panel.grid.minor = element_line(colour = "grey80", size = 0.2),
        text = element_text(size = 12),
        plot.title = element_text(hjust=0.5),
        axis.title = element_text(size = 13),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "in"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.25, r = 0, b = 0.25, l = 0, unit = "in"))

p_reservoir_data
```
