---
title: "Update Trandsducer Data - v2"
author: "Maddee Wiggins (FlowWest)"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

palette <- c("#999999", "#E69F00", "#56B4E9", "#F0E442", "#009E73", "#CC79A7")

```

## Source Data 

This script will compile all transducer data that is located in the `data-raw/surface_water/compensated_data` folder

First, source script:

TODO: note that `seconds` column is not reading in correctly. Check to make sure this is okay.

```{r echo=TRUE, message=FALSE, warning=FALSE}
source(here::here("analysis","surface_water", "run_all_files.R"))
```

```{r}
all_surface_water |> glimpse()
```

## Visualize and Explore Data 

Next, visualize the data to make sure everything appended and updated correctly.

```{r}
all_surface_water |> 
  group_by(name) |>
  summarise(min_date = min(datetime),
            max_date = max(datetime),
            n = n()) |> 
  knitr::kable()

```

### Water Depth

```{r fig.height=9, fig.width=11}
ggplot(data = all_surface_water, aes(x = datetime, y = depth_ft, color = name)) +     
  geom_line() + 
  scale_color_manual(values = palette) +
  labs(color = "Transducer Location", x = "Datetime", y = "Water Depth (ft)") +
  theme_minimal() 

```

### Pressure

```{r fig.height=9, fig.width=11}
ggplot(data = all_surface_water, aes(x = datetime, y = pressure_psi, color = name)) +     
  geom_line() + 
  scale_color_manual(values = palette) +
  labs(color = "Transducer Location", x = "Datetime", y = "Pressure (psi)") +
  theme_minimal()
```

### Temperature 

```{r fig.height=9, fig.width=11}
ggplot(data = all_surface_water, aes(x = datetime, y = temperature_f, color = name)) +     
  geom_line() + 
  scale_color_manual(values = palette) +
  labs(color = "Transducer Location", x = "Datetime", y = "Temperature (f)") +
  theme_minimal()

```

## By file type 

```{r fig.height=10, fig.width=15}
ggplot(all_surface_water, aes(datetime, y = depth_ft)) +
  geom_line(aes(color = name)) +
  scale_color_manual(values = palette) +
  theme_minimal() +
  facet_wrap(~file_name, ncol = 2) + 
  theme(strip.text = element_text(size = 10),
        legend.position = "bottom")

```

```{r}
# function
flag_datum_shift <- function(data, threshold = 1.0) {
  data |> 
    group_by(name) |> 
    arrange(datetime) |> 
    mutate(
      diff = c(NA, diff(depth_ft)),  
      flagged = ifelse(abs(diff) > threshold, TRUE, FALSE)  
    )
}


threshold <- 1  # Adjust threshold for your data
flagged_data <- flag_datum_shift(all_surface_water, threshold)


ggplot(flagged_data, aes(x = datetime, y = depth_ft)) +
  geom_line() +
  geom_point(data = flagged_data %>% filter(flagged), 
             aes(x = datetime, y = depth_ft), 
             color = "red", size = 3, shape = 8) +
  labs(x = "Time",
       y = "Depth (ft)",
       title = "Datum Shift Detection",
       subtitle = paste("Threshold for datum shift =", threshold, "ft")) +
  theme_minimal() +
  facet_wrap(~name)


flagged_data |>  
  filter(flagged) |> 
  select(name, datetime, depth_ft, diff, file_name)

```

```{r eval=FALSE, include=FALSE}
adjust_datum_shift <- function(data, threshold = 0.5) {
  # Ensure data is sorted by time
  tmp <- data  |>  
    group_by(name) |> 
    arrange(datetime) |> 
    mutate(depth_diff = c(0, diff(depth_ft))) |> 
    mutate(datum_shift = abs(depth_diff) > threshold)

  # Calculate the cumulative adjustment for each datum shift
  new_data <- tmp  |> 
    mutate(correction = cumsum(ifelse(datum_shift, -depth_diff, 0)),
           adjusted_depth = depth_ft + correction)
  
  return(new_data)
}

surface_water_correction <- adjust_datum_shift(all_surface_water, threshold = 0.5)

ggplot(surface_water_correction |> filter(name == "Bell Hill Rd"), aes(x = datetime)) +
  geom_line(aes(y = depth_ft), color = "red", linetype = "dashed") +  # Original data
  geom_line(aes(y = adjusted_depth), color = "blue") +                # Corrected data
  labs(
    title = "Surface Water Depth Adjustment for Datum Shifts",
    x = "Time",
    y = "Depth (ft)"
  ) +
  theme_minimal() +
  scale_y_continuous(labels = scales::comma)
```

## Save aggregated data 

Now save an Rdata file of aggregated surface water data in the `data/surface_water` folder

```{r}
all_surface_water |> saveRDS(here::here("data", "surface_water", "surface_water_data_aggregated.RDS"))

flagged_data |> 
  filter(flagged) |> 
  saveRDS(here::here('data', 'surface_water', 'surface_water_with_datum_shift_flags.RDS'))

```
