---
title: "ARCHIVE - method comparison"
author: "Maddee Rubenson (FlowWest)"
date: "`r Sys.Date()`"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)

options(digits = 15)  # Set to display 6 significant digits

```

**Method 2 `run_all_files.R` matches previous versions and records**

Compare two methods for data ingestion:

**Method 1**: Pull in legacy data from `data/surface_water` and append the new dataset to that

**Method 2**: Run all data within the `data-raw/surface_water/compensated_data` which includes new datasets

## Method 1

Read in data through `qc_data.R`

```{r include=FALSE}
source(here::here("analysis","surface_water", "qc_data.R"))
```

Combine the newly updated files:

```{r}
all_updated <- bind_rows(argonaut_updated, bellhill_updated, sodabay_updated, adobe_updated, highland_updated) |> 
  mutate(method = "method 1") |> 
  glimpse()
```

## Method 2

Read in the data through `run_all_files.R`

```{r include=FALSE}
source(here::here("analysis","surface_water", "run_all_files.R"))
```

```{r}
all_files_clean_method_2 <- all_files_clean |> 
  mutate(method = "method 2") |> 
  mutate(name = case_when(name == "Argonaut" ~ "Argonaut Rd",
                          name == "Adobe" ~ "Adobe Reservoir",
                          name == "Bell Hill" ~ "Bell Hill Rd",
                          name == "Highland" ~ "Highland Springs Reservoir",
                          name == "Soda Bay" ~ "Soda Bay Rd",
                          .default = as.character(name))) |> 
  glimpse()

```

## Method Comparison

**Take-a-ways**

-   The minimum and maximum dates are the same for all records except Adobe Reservoir

-   The number of records between the two methods is inconsistent for all transducers

```{r}

all_files <- all_files_clean_method_2 |> 
   bind_rows(all_updated) |> 
   mutate(temperature_f = signif(temperature_f, 15))

all_files |>  
  group_by(method, name) |>
  summarise(min_date = min(datetime),
            max_date = max(datetime),
            n = n()) |> 
  arrange(name) |> 
  knitr::kable()

```

### Adobe Reservoir

-   The first method is truncating the dataset (see table above)
-   All data that overlaps is the same

```{r}
all_files |> 
  filter(name == "Adobe Reservoir") |> 
  ggplot(aes(x = datetime, y = barometric_pressure_psi)) + 
  geom_line(aes(color = method)) +
  facet_wrap(~method)

method1_adobe <- all_files |> 
  filter(name == "Adobe Reservoir" & method == "method 1") 

method2_adobe <- all_files |> 
  filter(name == "Adobe Reservoir" & method == "method 2") 

# all rows that are in method 2 but NOT in method 1
do_not_match <- method1_adobe |> 
  select(-method, -file_name, -seconds) |> 
  anti_join(method2_adobe |> 
              select(-method, -seconds)) 

all_files |> filter(name == "Adobe Reservoir") |> filter(datetime == "2024-02-09 16:30:00") 

```

### Argonaut Rd

* There are `8536` more rows in Method 2 vs. Method 1
* Looking at the rows that do not match, their are inconsistencies with the `seconds` column
* Missing data that is included in Method 2 between 2020-02-01 and 2020-05-03
* The start and end dates are the same between the two methods

```{r}
all_files |> 
  filter(name == "Argonaut Rd") |> 
  ggplot(aes(x = datetime, y = barometric_pressure_psi)) + 
  geom_line(aes(color = method)) + facet_wrap(~method)

method1_arg <- all_files |> 
  filter(name == "Argonaut Rd" & method == "method 1") 

method2_arg <- all_files |> 
  filter(name == "Argonaut Rd" & method == "method 2") 

# all rows that are in method 2 but NOT in method 1
do_not_match <- method2_arg |> 
  select(-method, -file_name, -seconds) |> 
  anti_join(method1_arg |> 
              select(-method, -seconds)) 

do_not_match |>  
ggplot(aes(x = datetime, y = barometric_pressure_psi)) +
  geom_line()

do_not_match |> 
  summarise(min_date = min(datetime),
            max_date = max(datetime))

all_files |> 
  filter(name == "Argonaut Rd" & method == "method 1") |> 
  ggplot(aes(x = datetime, y = barometric_pressure_psi)) + 
  geom_line() + 
  geom_point(data = do_not_match, aes(x = datetime, y = barometric_pressure_psi), color = 'pink', alpha = 0.1) 

```

### Bell Hill Rd

* all the differences are within the year 2020

```{r}
all_files |> 
  filter(name == "Bell Hill Rd") |> 
  ggplot(aes(x = datetime, y = barometric_pressure_psi)) + 
  geom_line(aes(color = method)) + facet_wrap(~method)

method1_bell <- all_files |> 
  filter(name == "Bell Hill Rd" & method == "method 1") 

method2_bell <- all_files |> 
  filter(name == "Bell Hill Rd" & method == "method 2")# |> 
  #filter(datetime == "2020-01-01 19:00:15")

# all rows that are in method 2 but NOT in method 1
do_not_match <- method2_bell |> 
  select(-method, -file_name, -seconds) |> 
  anti_join(method1_bell |> 
              select(-method, -seconds)) 

# bell_1 <- method1_bell |> filter(datetime == "2023-11-01 13:00:00")
# bell_2 <- method2_bell |> filter(datetime == "2023-11-01 13:00:00")
# 
# bell_1
# bell_2

do_not_match |>  
ggplot(aes(x = datetime, y = barometric_pressure_psi)) +
  geom_line()

do_not_match |> 
  summarise(min_date = min(datetime),
            max_date = max(datetime))

all_files |> 
  filter(name == "Bell Hill Rd" & method == "method 1") |> 
  ggplot(aes(x = datetime, y = barometric_pressure_psi)) + 
  geom_line() + 
  geom_point(data = do_not_match, aes(x = datetime, y = barometric_pressure_psi), color = 'pink', alpha = 0.1) 

```

`r knitr::knit_exit()`

Explore differences between the two methods

```{r}
all_files |> 
  group_by(year(datetime), month(datetime), day(datetime), method, name) |> 
  summarise(n = n()) |> 
  ggplot() + 
  geom_col(aes(x = as.factor(`year(datetime)`), y = n, fill = method), position = "dodge") + 
  facet_wrap(~ name) +
  coord_flip() +
  theme_minimal()

all_files |> 
  filter(year(datetime) == 2020) |> 
  filter(name %in% c("Argonaut Rd", "Bell Hill Rd")) |> 
  group_by(year(datetime), month(datetime), day(datetime), method, name) |> 
  summarise(n = n()) |> 
  ggplot() + 
  geom_col(aes(x = as.factor(`month(datetime)`), y = n, fill = method), position = "dodge") + 
  facet_wrap(~ name) +
  coord_flip() +
  theme_minimal()

all_files |> 
  filter(year(datetime) == 2020) |> 
  filter(name %in% c("Argonaut Rd", "Bell Hill Rd")) |> 
  group_by(year(datetime), month(datetime), day(datetime), method, name) |> 
  summarise(n = n()) |> 
  ggplot() + 
  geom_col(aes(x = as.factor(`day(datetime)`), y = n, fill = method), position = "dodge") + 
  facet_wrap(~ name) +
  coord_flip() +
  theme_minimal()

all_files |> 
  filter(year(datetime) == 2020 & day(datetime) == 1 & month(datetime) == 1) |> 
  filter(name %in% c("Argonaut Rd")) |> 
  arrange(datetime) 
# Method 2 has data betwen 2020-01-01 23:00:15 and 2020-01-01 23:15:00 AND and 2020-01-01 23:15:15 to 2020-01-01 23:30:00
# that does not exist in Method 1 

all_files |> 
  filter(year(datetime) == 2020 & day(datetime) == 1 & month(datetime) == 1) |> 
  filter(name %in% c("Argonaut Rd", "Bell Hill Rd")) |> 
  ggplot() + 
  geom_line(aes(x = datetime, y = depth_ft, color = method)) +
  facet_wrap(~name) +
  theme_minimal()

all_files |>
  filter(name == "Argonaut Rd") |>
  filter(year(datetime) == 2020) |> 
  ggplot(aes(x = datetime, y = depth_ft, color = method, alpha = 0.5)) +
  geom_line() +
  labs(color = "Transducer Location", x = "Datetime", y = "Water Depth (ft)") +
  theme_minimal() +
  facet_wrap(~name + method)
```

```{r}
all_files |>
  # filter(name == "Argonaut Rd") |>
  # filter(year(datetime) == 2020) |> 
  ggplot(aes(x = datetime, y = depth_ft, color = method, alpha = 0.5)) +
  geom_line() +
  labs(color = "Transducer Location", x = "Datetime", y = "Water Depth (ft)") +
  theme_minimal() +
  facet_wrap(~name)

all_files |> 
  ggplot(aes(x = datetime, y = temperature_f, color = method,alpha = 0.5)) +     
  geom_line() + 
  labs(color = "Transducer Location", x = "Datetime", y = "Temperature (F)") +
  theme_minimal() + 
  facet_wrap(~name)

all_files |>
  ggplot(aes(x = datetime, y = pressure_psi, color = method, alpha = 0.5)) +
  geom_line() +
  labs(color = "Transducer Location", x = "Datetime", y = "Pressure (PSI)") +
  theme_minimal() +
  facet_wrap(~name)

```
